Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-24 paper/verification-conditions.tex
Add minor revisions to section 3

The AGREE specification language, and semantics, are inspired by the Lustre language \cite{10.1145/41625.41641}.
Lustre reasons over a synchronous dataflow model where the inputs and outputs of
components are streams.
Informally, streams assign values to expressions at each point in time.
AGREE contracts express relationships between input and output streams by assuming a set of allowed input streams and then guaranteeing a corresponding set of allowed output streams.
Output for streams not included in the assumed input is undefined.

@@

PLTL is a logic enhanced with temporal operators able to
reason about the truth values of formulas through time.
It combines past-time operators that reason over the history of computation up to a point (PTLTL) and future-time operators that reason over the computation that follows that point (LTL).
Its semantics
are defined relative to a point in time $i$ and a finite trace of
system states $\pi = s_0, s_1, \ldots, s_i$.

@@

A \emph{system} is a tuple $(\inputs, \outputs, \assumes,
\guarantees,C)$, where $\inputs$ is the input set, $\outputs$ is the
output set, $\assumes$ is the set of assumptions, $\guarantees$ is the
set of guarantees, and $C$ are subcomponents.  A subcomponent
$\component$ is, hierarchically, also a system, and may be designated
by its own tuple $(\inputs_\component, \outputs_\component,
\assumes_\component, \guarantees_\component, C_c)$.  From the
components and their connections, $\mathbb{I}_\component$ is defined
to be the set of components providing input to some component
$\component$ in the system, and $\mathbb{O}$ is defined to be the set
of components that provide the output for the system.

A system $S$ is
\emph{correct} if and only if for all components $c \in C$ the
following two verification conditions hold:
\begin{equation}\label{eq:assumes}
            \globally(\historically(\assumes \wedge
            \bigwedge_{\component^\prime \in \mathbb{I}_\component} P_{\component^\prime})
            \implies \assumes_\component)
\end{equation}
\begin{equation}\label{eq:guarantees}
            \globally(\historically(\assumes \wedge
            \bigwedge_{\component^\prime \in \mathbb{O}} \guarantees_{\component^\prime})
            \implies \guarantees)
\end{equation}
The conditions from \eqref{eq:assumes} verify the input assumptions on each component under
the system assumptions and upstream component guarantees.  They check
if the component guarantees and system assumptions are strong enough
to imply input assumptions on all immediate downstream components.
The condition in \eqref{eq:guarantees} checks the output guarantees of the system under the
system assumptions and component guarantees that provide the output.
It checks if the guarantees on components providing primary outputs
are strong enough to imply the system guarantees.

If all the verification conditions hold (AGREE uses $k$-inductive
model checking to automatically prove or disprove each generated
verification condition), then the system is said to be \emph{correct},
meaning that the system composition meets input assumptions at each
input as well as the guarantees on the system output. A consequence of
this result is that $\globally(\historically(\assumes) \implies
\guarantees)$ holds for the system contract.
In this way the Liskhov substitution principle applies meaning that the implementation is a safe substitution for the system contract \cite{10.1145/62139.62141}.

>>>>

The AGREE specification language, and semantics, are inspired by the Lustre language \cite{10.1145/41625.41641}.
Lustre reasons over a synchronous data-flow model where the inputs and outputs of
components are streams.
Informally, streams assign values to expressions at each point in time.
AGREE contracts express relationships between input and output streams by assuming a set of allowed input streams and then guaranteeing a corresponding set of allowed output streams.
Output for streams not included in the assumed input is undefined.

@@

PLTL is a logic enhanced with temporal operators able to
reason about the truth values of formulas through time.
It combines past-time operators that reason over the history of computation up to a point (PTLTL) and future-time operators that reason over the computation that follows that point (LTL).
Its semantics
are defined relative to a point in time $i$, a finite trace of
system states $\pi = s_0, s_1, \ldots, s_i$, and some logic formula $f$.

@@

A \emph{system} is a tuple $(\inputs, \outputs, \assumes,
\guarantees,C)$, where $\inputs$ is the input set, $\outputs$ is the
output set, $\assumes$ is the set of assumptions, $\guarantees$ is the
set of guarantees, and $C$ are subcomponents.  Assumptions and guarantees only use the past-time operators from PLTL. A subcomponent
$\component$ is, hierarchically, also a system, and may be designated
by its own tuple $(\inputs_\component, \outputs_\component,
\assumes_\component, \guarantees_\component, C_c)$.  From the
components and their connections, $\mathbb{I}_\component$ is defined
to be the set of components providing input to some component
$\component$ in the system, and $\mathbb{O}$ is defined to be the set
of components that provide the output for the system.

A system is
\emph{correct} if and only if for all components $c \in C$ the
following two verification conditions hold:
\begin{equation}\label{eq:assumes}
            \globally(\historically(\assumes \wedge
            \bigwedge_{\component^\prime \in \mathbb{I}_\component} P_{\component^\prime})
            \implies \assumes_\component)
\end{equation}
\begin{equation}\label{eq:guarantees}
            \globally(\historically(\assumes \wedge
            \bigwedge_{\component^\prime \in \mathbb{O}} \guarantees_{\component^\prime})
            \implies \guarantees)
\end{equation}
The conditions from \eqref{eq:assumes} verify the input assumptions on each component under
the system assumptions and upstream component guarantees.  They check
if the component guarantees and system assumptions are strong enough
to imply input assumptions on all immediate downstream components.
The condition in \eqref{eq:guarantees} checks the output guarantees of the system under the
system assumptions and component guarantees that provide the output.
It checks if the guarantees on components providing primary outputs
are strong enough to imply the system guarantees.

If all the verification conditions hold (AGREE uses $k$-inductive
model checking to automatically prove or disprove each generated
verification condition), then the system is said to be \emph{correct},
meaning that the system composition meets input assumptions at each
input as well as the guarantees on the system output. A consequence of
this result is that $\globally(\historically(\assumes) \implies
\guarantees)$ holds for the system contract.
Therefore the Liskhov substitution principle applies, and as such, the implementation is a safe substitution for the system contract \cite{10.1145/62139.62141}.
